---
title: "Sækja gögn"
---


# Tvíkosta atriði (dichotomous)

## Dataset PISA Mathematics

### Sækja gögn
```{r}
#| warning: false
#| echo: false
dat <- readr::read_csv("data/pisa_math.csv")

dat  |> 
  downloadthis::download_this(
    output_name = "pisa_math.csv",
    output_extension = ".csv",
    button_label = "pisa_math.csv",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-file-csv"
  )
```


### Atriðasafn
Dæmi frá 565 Austurískum nemendum sem tóku PISA 2009 -- verkefni úr hluta M3.

Svarkvarði: (0=rangt, 1=rétt)

[^1]

[^1]: gögn sótt af <https://cran.r-project.org/web/packages/sirt/index.html>


# Fjölkosta atriði (Polytomous)
## Rosenberg Self-Esteem Scale

### Sækja gögn
```{r}
#| warning: false
#| echo: false
dat <- readr::read_csv("data/Rosenberg.csv")

dat  |> 
  downloadthis::download_this(
    output_name = "Rosenberg.csv",
    output_extension = ".csv",
    button_label = "Rosenberg.csv",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-file-csv"
  )
```


### Atriði
Q1. I feel that I am a person of worth, at least on an equal plane with others. Q2. I feel that I have a number of good qualities.\
Q3. All in all, I am inclined to feel that I am a failure.\
Q4. I am able to do things as well as most other people.\
Q5. I feel I do not have much to be proud of.\
Q6. I take a positive attitude toward myself.\
Q7. On the whole, I am satisfied with myself.\
Q8. I wish I could have more respect for myself.\
Q9. I certainly feel useless at times.\
Q10. At times I think I am no good at all.

Svarkvarði: (1=strongly disagree, 2=disagree, 3=agree, and 4=strongly)

[^2]

[^2]: gögn sótt af <https://openpsychometrics.org/_rawdata/>

